Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-13 paper/paper.qmd
Update theta notation in fig caption
Fix: inline citation

Depths for each reef were extracted using 10m resolution bathymetry data made available in
GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched with the 3806
reef outlines through geometric intersection. All depth values were converted to positive
values (depths below sea level). The median depth was used to provide an indicative depth
value for each reef. While the bathymetry data are said to be accurate up to 15m from Mean
Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used
for this study. Notably, bathymetry data were derived from satellite imagery and can be
limited in their alignment with the established GBRMPA reef outlines used to characterise
reef locations and their areal extent. Further limitations are outlined in the Discussion.
Code to extract depth estimates, and the resulting depth estimates themselves, are available
at [@iwanaga2025].

@@

![Scatter plot indicating reef median depth (metres) and log10 weighted incoming
connectivity for each reef. Point colours represent the median number of years each reef
maintains positive carbonate budgets across $theta$ values from 10-20% live coral cover.
Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
fig-align="center" width="14.82cm"}

>>>>

Depths for each reef were extracted using 10m resolution bathymetry data made available in
GBRMPA [-@GBRMPA2020]. For each reef, bathymetry data were spatially matched with the 3806
reef outlines through geometric intersection. All depth values were converted to positive
values (depths below sea level). The median depth was used to provide an indicative depth
value for each reef. While the bathymetry data are said to be accurate up to 15m from Mean
Sea Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used
for this study. Notably, bathymetry data were derived from satellite imagery and can be
limited in their alignment with the established GBRMPA reef outlines used to characterise
reef locations and their areal extent. Further limitations are outlined in the Discussion.
Code to extract depth estimates, and the resulting depth estimates themselves, are available
at @iwanaga2025.

@@

![Scatter plot indicating reef median depth (metres) and log10 weighted incoming
connectivity for each reef. Point colours represent the median number of years each reef
maintains positive carbonate budgets across $\theta$ values from 10-20% live coral cover.
Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
fig-align="center" width="14.82cm"}
